---
title: "PSTAT 175 Project"
author: "Emily Zhuang"
date: "10/31/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/ezhuang/Downloads")
```

```{r}
library(survival)
data(kidney)
#create survival vector
survival_vec <- Surv(kidney$time,kidney$status)
### fit kaplan meier curve
fit <- survfit(survival_vec ~ 1)
plot(kidneyfit, xlab = "Time", ylab = "S(t)", main = "Kaplan Meier Curve for Time Until")
```

```{r}
library(KMsurv)
data(pneumon)
pneumon

library(bayesSurv)
data(tandmob2)
tandmob2

library(survival)
data(bladder1)
bladder1
?bladder1

data(colon)
colon
?colon

kidney
```

```{r}
library(survival)
library(tidyverse)
CPTAC_tibble_clean <- as_tibble(CPTAC) |>
  filter(disease_type=="Adenomas and Adenocarcinomas") |>
  drop_na(diag__days_to_recurrence) |>
  drop_na(demo__vital_status)

CPTAC_tibble_clean

CPTAC_tibble_clean$demo__vital_status[CPTAC_tibble_clean$demo__vital_status == "Dead"] <- as.numeric(1)
CPTAC_tibble_clean$demo__vital_status[CPTAC_tibble_clean$demo__vital_status == "Alive"] <- as.numeric(0)
CPTAC_tibble_clean$demo__vital_status[CPTAC_tibble_clean$demo__vital_status == "Not Reported"] <-as.numeric(0)

CPTAC_tibble_clean$demo__vital_status <- as.numeric(as.character(CPTAC_tibble_clean$demo__vital_status))

survival_vec <- Surv(CPTAC_tibble_clean$diag__days_to_recurrence, CPTAC_tibble_clean$demo__vital_status)
### fit kaplan meier curve
fit <- survfit(survival_vec ~ 1)
### plot kaplan meier curve
plot(fit, main = "Kaplan Meier Curve for Time Until Recurrence of Disease", xlab = "Days", ylab = "S(t)")

```
survival Package
bladder1: Data on recurrences of bladder cancer, used by many people to demonstrate methodology for recurrent event modelling

cgd : Data are from a placebo controlled trial of gamma interferon in chronic granulotomous disease (CGD).

colon: Data on the effectiveness of chemotherapy on colon cancer.

mgus : Natural history of 241 subjects with monoclonal gammapothy of undetermined significance (MGUS).

nwtco: Data from the National Wilm’s Tumor Study.

KMsurv Package
After loading the package, you will to call data(datasetname) in order to access these data sets.

bfeed: Data on the duration of breast feeding.

burn: Data on the treatment of burn victims. (Source LinkLinks to an external site.)

larynx: Survival data for larynx cancer patients at different stages and ages.

pneumon: Study on the age of children that had pneumonia.

std: Study of the time until re-infection for STD patients including many covariates.

bayesSurv Package
tandmob2: Belgian study of the dental health of over 4,000 primary school children. You will need to call data(tandmob2) in order to access this data set.